peter_plots

### 2024-12-03 peter_EDA.qmd
updating recoding script

```{r}
dataset_clean <- dataset_clean %>% mutate(educ = case_when(S13 == "(1) Grades 1-8" ~ "No college experience",
                                                           S13 == "(2) Some High School, but did not graduate" ~ "No college experience",
                                                           S13 == "(3) High School graduate or GED" ~ "No college experience",
                                                           S13 == "(4) Some college" ~ "Some college experience",
                                                           S13 == "(5) Associates, 2-year degree" ~ "College graduate",
                                                           S13 == "(6) Bachelors, 4-year degree" ~ "College graduate",
                                                           S13 == "(7) Post-graduate degree" ~ "College graduate"),
                                          sex_orientation = case_when(S3 == "(01) Straight, that is, not gay or lesbian" ~ "Straight",
                                                                     S3 == "(02) Gay or lesbian" ~ "Queer",
                                                                     S3 == "(03) Bisexual" ~ "Queer",
                                                                     S3 == "(04) Something else (Specify)" ~ "Queer",
                                                                     S3 == "(88) Refused" ~ "Refused/Don't Know",
                                                                     S3 == "(99) I don" ~ "Refused/Don't Know"),
                                          rural = case_when(S14 == "(1) Large urban area" ~ "Urban/suburban",
                                                            S14 == "(2) Large suburb near large city" ~ "Urban/suburban",
                                                            S14 == "(3) Small suburb near small town or city" ~ "Urban/suburban",
                                                            S14 == "(4) Small town or small city" ~ "Urban/suburban",
                                                            S14 == "(5) Rural area" ~ "Rural"))
```

@@

```{r}
#save(dataset_clean, file = "/Users/pdeguz01/Documents/git/Data/2020 CMPS/Output/2020cmps_clean.RData")

@@

| Level of Interest in Politics     | Percent of Total Respondents  |
|-----------------------------------|-------------------------------|
| Very interested in politics       | 24.54%                        |
| Somewhat interested               | 43.39%                        |
| Not that interested in politics   | 20.76%                        |
| Not at all interested in politics | 11.31%                        |

>>>>

dataset_clean <- dataset_clean %>% mutate(educ = case_when(S13 == "(1) Grades 1-8" ~ "No college experience",
                                                           S13 == "(2) Some High School, but did not graduate" ~ "No college experience",
                                                           S13 == "(3) High School graduate or GED" ~ "No college experience",
                                                           S13 == "(4) Some college" ~ "Some college experience",
                                                           S13 == "(5) Associates, 2-year degree" ~ "College graduate",
                                                           S13 == "(6) Bachelors, 4-year degree" ~ "College graduate",
                                                           S13 == "(7) Post-graduate degree" ~ "College graduate"),
                                          sex_orientation = case_when(S3 == "(01) Straight, that is, not gay or lesbian" ~ "Straight",
                                                                     S3 == "(02) Gay or lesbian" ~ "Queer",
                                                                     S3 == "(03) Bisexual" ~ "Queer",
                                                                     S3 == "(04) Something else (Specify)" ~ "Queer",
                                                                     S3 == "(88) Refused" ~ "Refused/Don't Know",
                                                                     S3 == "(99) I don" ~ "Refused/Don't Know"),
                                          rural = case_when(S14 == "(1) Large urban area" ~ "Urban/suburban",
                                                            S14 == "(2) Large suburb near large city" ~ "Urban/suburban",
                                                            S14 == "(3) Small suburb near small town or city" ~ "Urban/suburban",
                                                            S14 == "(4) Small town or small city" ~ "Urban/suburban",
                                                            S14 == "(5) Rural area" ~ "Rural"),
                                          white = case_when(S2_RACE_PRIME == "(1) White" ~ "White", 
                                                            S2_RACE_PRIME == "(2) Hispanic or Latino" ~ "Non-White",
                                                            S2_RACE_PRIME == "(3) Black or African American" ~ "Non-White",
                                                            S2_RACE_PRIME == "(4) Asian American" ~ "Non-White",
                                                            S2_RACE_PRIME == "(5) American Indian/Native American" ~ "Non-White",
                                                            S2_RACE_PRIME == "(6) Arab, Middle Eastern or North African" ~ "Non-White",
                                                            S2_RACE_PRIME == "(7) Native Hawaiian" ~ "Non-White",
                                                            S2_RACE_PRIME == "(8) Not Hawaiian, but other Pacific Islander" ~ "Non-White"),
                                          race_recoded = case_when(S2_RACE_PRIME == "(1) White" ~ "White",
                                                                   S2_RACE_PRIME == "(2) Hispanic or Latino" ~ "Latino",
                                                                   S2_RACE_PRIME == "(3) Black or African American" ~ "Black",
                                                                   S2_RACE_PRIME == "(4) Asian American" ~ "Asian American",
                                                                   S2_RACE_PRIME == "(5) American Indian/Native American" ~ "AIAN",
                                                                   S2_RACE_PRIME == "(6) Arab, Middle Eastern or North African" ~ "Arab/MENA",
                                                                   S2_RACE_PRIME == "(7) Native Hawaiian" ~ "NHPI",
                                                                   S2_RACE_PRIME == "(8) Not Hawaiian, but other Pacific Islander" ~ "NHPI"))

@@

```{r}
save(dataset_clean, file = "/Users/pdeguz01/Documents/git/Data/2020 CMPS/Output/2020cmps_clean.RData")

@@

| Level of Interest in Politics     | Percent of Total Respondents |
|-----------------------------------|------------------------------|
| Very interested in politics       | 24.54%                       |
| Somewhat interested               | 43.39%                       |
| Not that interested in politics   | 20.76%                       |
| Not at all interested in politics | 11.31%                       |

### 2024-12-03 peter_plots.qmd
updating recoding script

##

# Loading data

# plot 1:

# plot 2:

# plot 3:

>>>>

## 
# Packages
```{r}
library(tidyverse)
library(janitor)
library(ggplot2)
library(scales)
```

# Loading data
```{r}
file_path = "/Users/pdeguz01/Documents/git/Data/2020 CMPS/Output/2020cmps_clean.RData"
load(file_path)
```

# plot 1:
Race and importance of being a member of racial group to identity (Q271)
```{r}

data_summary <- dataset_clean %>%
  group_by(S2_RACE_PRIME, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

races <- unique(data_summary$S2_RACE_PRIME)

# Loop through each race and generate a plot
for (race_value in races) {
  plot_data <- data_summary %>% filter(S2_RACE_PRIME == race_value)

  p <- ggplot(plot_data, aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for", race_value, "Respondents"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", race_value, ".png"), plot = p, width = 6, height = 4)

  # Print the plot (optional, if you want to view them in the R console)
  print(p)
}

```

# plot 2:
Race and interest in politics (Q29)
```{r}

```

# plot 3:
White/non-white and importance of race to identity (Q271)

# plot:
White/non-white and interest in politics (Q29)

# plot 3:
College Experience and importance of being a member of racial group to identity (Q271)
```{r}
data_summary <- dataset_clean %>%
  group_by(educ, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

plot_somecollege <- data_summary %>% filter(educ == "Some college experience") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with Some college Experience"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_somecollege)

plot_nocollege <- data_summary %>% filter(educ == "No college experience") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with No college Experience"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_nocollege)

```

# plot 4:
College Experience and interest in politics (Q29)
```{r}

```

# plot 4:
Age and importance of being a member of racial group to identity (Q271)
```{r}

```

# plot 5:
Age and interest in politics (Q29)
```{r}

```

# plot 6:
Rurality and importance of being a member of racial group to identity (Q271)
```{r}

```

# plot 7:
Rurality and interest in politics
```{r}

```
